### 2017-06-06 paper/documents/4.experiment.tex
- update paper

We applied feature normalization on this paper in order to enhance high accuracy.

>>>>

An approach of \textit{Feature Normalization} to enhance the accuracy result proved by Singh \cite{singh2015investigations}. We applied feature normalization on this paper to cross check if this methodology can help to tweak accuracy of classification results. Various normalization techniques in this study are:

\textbf{Z-Score Normalization}, A very common techniques to normalize the feature to zero mean and unit variance is Z-score normalization \cite{jayalakshmi2011statistical}. It is a linear technique which initially mean ( \(\bar{x}\) ) and standard deviation ( \(\sigma\) ) of the specific feature values are computed using:

\begin{equation}
\bar{x}=\frac{1}{N}\sum_{i-1}^{N}x_{i}
\end{equation}

and,
\begin{equation}
\sigma^2=\frac{1}{N-1}\sum_{i-1}^{N}(x_{i}-\bar{x})^2
\end{equation}

the normalized feature is then given by:
\begin{equation}
\bar{x}_i=\frac{x_i-\bar{x}}{\sigma}
\end{equation}

\textbf{Min-Max Normalization}, This technique performs a linear transformation on the original data. For mapping a value, of an attribute \(x_i\) from range [min(\(x_i\)), max(\(x_i\))] to a new range [min \(x_new,\),max \(x_new\), the normalized feature is given by:

\begin{equation}
\hat{x}_i=\frac{X_i-min(x_i)}{max(x_i)-min(x_i)}
\end{equation}

The advantage of Min-Max normalization is that it preserves the relationship among the original data values \cite{manikandan2013achieving}. In this study \(max\,x_{new}=1\) and \(min\,x_{new}=-1\) is used.

\textbf{Linar Scaling to Unit Range}, This is also a linear transformation technique to normalize data in range[0,1]. Given a lower bound min(\(x_i\)) and upper bound max(\(x_i\)) of an attribute \(x_i\), the normalized value is given by:

\begin{equation}
\hat{x}_i=\frac{x_i-min(x_i)}{max(x_i)-min(x_i)}
\end{equation}

Linear scaling to unit range is special case of min-max normalization in which max\(\,x_{new}\)=1 and min\(\,x_{new}\)=0.

\textbf{Softmax Scaling}, In addition to linear scaling, non linear normalization techniques may be used in cases where data are not evenly distributed around the mean \cite{theodoridis2010introduction}. In such cases the transformations based on nonlinear (i.e., exponential, logarithmic, sigmoid etc) functions can be used to map the data within specified intervals. One such popular technique is so called softmax scaling which squashes the data value non linearly in the interval [0,1]. the normalized feature is given by;

\begin{equation}
\hat{x}_i=\frac{1}{1+e^{-y}}
\end{equation}

where \(y=\frac{x_i-\bar{x}}{r\sigma}\) and \textit{r} is a user defined parameter. in the above equation that for small values of y i.e., for values of \(x_i\) closer to mean, y is an approximately linear function. Values away from mean are squashed exponentially.

### 2017-06-06 paper/documents/5.conclusion.tex
- update paper

\section{CONCLUSION}
\label{sec:conclusion}

This is conclusion

>>>>

\section{Results and Conclusion}
\label{sec:conclusion}

\subsection{Result}
\label{sec:results}

We trained and evaluated several different classifier using 10-fold cross-validation and independent test on our data set. The classifiers was based on existing works and complemented by commonly used classification approaches. It included: \textit{Random forest decision trees}, \textit{logistic regression}, \textit{support vector machines with sequential minimal optimization}, \textit{naive bayes classifier}, and \textit{bayesian networks}. We are using WEKA library and tool for the technical platform. The classifiers were evaluated according to several established performance metric (accuracy, mean absolute error (MAE) \cite{willmott2005advantages}, and area under ROC (AUC) \cite{huang2005using}.

\renewcommand{\arraystretch}{1.5}
\setlength{\tabcolsep}{8pt}
\begin{table}[]
\centering
\caption{Summary of 10-fold cross -validation and independent test accuracies with feature normalization data set.}
\label{table:table2}
\resizebox{0.5\textwidth}{!}{%
\begin{tabular}{|l|l|l|l|l|}
\hline
\multicolumn{1}{|c|}{\textbf{Full Classes}}    & \multicolumn{2}{c|}{\textbf{10-Folds Cross Validation}} & \multicolumn{2}{c|}{\textbf{Independent Test}} \\ \hline
Original                                       & Random forest                 & 89.37\%                 & Random forest                & 88.54\%         \\ \hline
Linear Scale                                   & Random forest                 & 89.77\%                 & Logistic Regression          & 81.65\%         \\ \hline
Min-Max Normalization                          & Random forest                 & 89.53\%                 & Logistic Regression          & 81.65\%         \\ \hline
Softmax Scaling                                & Random forest                 & 80.13\%                 & Random forest                & 79.81\%         \\ \hline
Z-Score Normalization                          & Random forest                 & 89.68\%                 & Random forest                & 86.52\%         \\ \hline
\multicolumn{1}{|c|}{\textbf{Reduced Classes}} & \multicolumn{2}{c|}{\textbf{10-Folds Cross Validation}} & \multicolumn{2}{c|}{\textbf{Independent Test}} \\ \hline
Original                                       & Random forest                 & 94.52\%                 & Random forest                & 93.53\%         \\ \hline
Linear Scale                                   & Random forest                 & 94.33\%                 & Random forest                & 88.48\%         \\ \hline
Min-Max Normalization                          & Random forest                 & 94.39\%                 & Random forest                & 88.78\%         \\ \hline
Softmax Scaling                                & Random forest                 & 92.59\%                 & Random forest                & 92.34\%         \\ \hline
Z-Score Normalization                          & Random forest                 & 89.40\%                 & Random forest                & 92.10\%         \\ \hline
\end{tabular}%
}
\end{table}

Table \ref{table:table2} list the highest accuracy from 10-fold cross-validation and independent test of our works. Random forest is the most stable with good performance from our works. The accuracy result also reasonable. it means the good accuracy is not over fitting after checking the cross-validation with the independent test results.

\renewcommand{\arraystretch}{1.5}
\setlength{\tabcolsep}{8pt}
\begin{table}[]
\centering
\caption{Comparison with previous works.}
\label{table:table3}
\resizebox{0.5\textwidth}{!}{%
\begin{tabular}{|c|c|c|c|c|c|c|}
\hline
\textbf{Classifier}             & \multicolumn{2}{c|}{\textbf{Accuracy}} & \multicolumn{2}{c|}{\textbf{Mean Absolute Error}} & \multicolumn{2}{c|}{\textbf{Wgt. Avg. AUC}} \\ \hline
\textbf{Full set of classes}    & *                  & **                & *                       & **                      & *                    & **                   \\ \hline
Random Forest                   & 76.27\%            & 89.37\%           & 0.0905                  & 0.0691                  & 0.943                & 0.984                \\ \hline
Logistic Regression             & 75.85\%            & 82.64\%           & 0.0826                  & 0.1013                  & 0.947                & 0.962                \\ \hline
SMO                             & 75.28\%            & 81.65\%           & 0.1753                  & 0.2503                  & 0.926                & 0.91                 \\ \hline
Bayesian Networks               & 72.03\%            & 70.54\%           & 0.0801                  & 0.122                   & 0.933                & 0.927                \\ \hline
Naive Bayes                     & 70.76\%            & 74.43\%           & 0.0769                  & 0.1055                  & 0.933                & 0.95                 \\ \hline
\textbf{Reduced set of classes} & *                  & **                & *                       & **                      & *                    & **                   \\ \hline
Bayesian Networks               & 96.58\%            & 92.61\%           & 0.0322                  & 0.0919                  & 0.995                & 0.973                \\ \hline
SMO                             & 96.15\%            & 88.15\%           & 0.2308                  & 0.1185                  & 0.975                & 0.875                \\ \hline
Logistic Regression             & 96.15\%            & 88.15\%           & 0.0381                  & 0.1662                  & 0.993                & 0.953                \\ \hline
Naive Bayes                     & 95.58\%            & 89.84\%           & 0.0383                  & 0.2319                  & 0.994                & 0.89                 \\ \hline
Random Forest                   & 91.17\%            & 94.52\%           & 0.1182                  & 0.0916                  & 0.985                & 0.987                \\ \hline
\end{tabular}%
}
\end{table}

Table \ref{table:table3}, comparison result of our works with previous works. Which is our works is quite better in full set classes. Random forest still dominating for the accuracy result.

\subsection{Conclusion}
\label{sec:conclusion}

Not yet :v
